---
title       : Intro to R markdown
subtitle    : Analysis and Visualization of Large Scale Datasets (ICESI)
author      : Carlos Ignacio Patiño (cpatinof@gmail.com)
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : mathjax            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Markdown: Intro

- Markdown is a text-to-HTML conversion tool for web writers
- It allows you to write using an easy-to-read, easy-to-write plain text format, then convert it to structurally valid XHTML (or HTML)

--- .class #id 

## Markdown: Basic Syntax

Headings

```{r, echo=TRUE}
## Secondary heading
### Tertiary heading
```

## Secondary heading
### Tertiary heading

--- .class #id

## Lists

- For unordered lists use "*"
- For oredered lists use numbers "1.", "2.", and so on

```{r, echo=TRUE, eval=FALSE}
* first element
* second element
* third element
```

* first element
* second element
* third element

--- .class #id

## R Markdown

* Allows the user to create dynamic documents with embedded R code
* Use markdown language and R code chunks in the same document
* R code can be echoed and executed
* Export to html or pdf
* Create presentations

--- .class #id

## R Markdown demo

* Creating R md file from R Studio
* Headings
* Inserting code and code options
* In-line code
* $LaTeX$ equations
* Tables using `pander`
* Creating html and pdf